
You can start a course on Leanpub and come back at any time. 

1. First, click on the course you want to take. You can then drag the slider or type in a number for the price you want to pay.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "The price slider is highlighted."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b34b732d40_2_34")
    ```

1. Click "Add Course to Cart". You will need to do this even if you take the course for free.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "The button is highlighted on the Cluster 101 course landing page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_40")
    ```

1. Click "Checkout with Free Purchase" if you are taking the course for free.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "The checkout with free purchase button is highlighted."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_47")
    ```

1. Click "Complete Free Purchase".

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "The complete free purchase button is highlighted."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_54")
    ```

1. This takes you back to the home page, which can be a bit confusing! You can get back to the course by clicking the hamburger menu, selecting "Library", and "Courses". You can also go directly to https://leanpub.com/user_dashboard/courses.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_61")
    ```

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "The library tab and courses sub-tab are highlighted from the dropdown hamburger menu."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_68")
    ```

1. You should see your course listed in your "Courses" tab.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub courses page lists one course, CLuster 101."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_75")
    ```

1. Click on the course, and click "Go to course".

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Cluster 101 course has been expanded and now shows a 'go to course' option."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_89")
    ```

1. Click "Start the Course".

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "The course landing page now has the option to start the course."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_99")
    ```

