
# (PART\*) Guide for Learners {-}

# About Leanpub

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_about_leanpub.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Make a Leanpub Account

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_make_an_account.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Find a Course

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_find_a_course.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

:::: {.notice}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_hutch_homepage.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```
::::

# Start a Course

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_start_a_course.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Navigate a Course

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_navigate_a_course.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Get a Certificate of Completion

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/learner_get_a_certificate.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# (PART\*) Guide for Developers {-}

# Developer Roles

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/developer_roles.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Organizational Accounts

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/developer_organization_account.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Confirm your Role

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/developer_confirm_role.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# (PART\*) Guide for Authors {-}

# Create a Course

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/author_create_course.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# (PART\*) Guide for Editors {-}

# Add Organization Author

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/editor_add_author.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Add Organization Editor

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/editor_add_editor.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Invite an Author's Course

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/editor_invite_course.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```

# Add a Course as an Editor

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/editor_create_course.Rmd",
  branch = "formatting",
  repo_name = "fhdsl/Using_Leanpub"
)
```



