
:::: {.warning}
_Before proceeding you should:_

1. Make sure that you have verified your email. Go to https://leanpub.com/author_dashboard/courses/unpublished and click the link to resend a verification email if you haven't yet verified your account.

    ```{r, echo=FALSE, fig.alt='If our email has not been verified, we get a landing page that requests we do this. There is a link to resend verification.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_89")
    ```
::::

1. Go to https://leanpub.com/create/course. If your page looks different from below, make sure your email is verified (above). 

    ```{r, echo=FALSE, fig.alt='The strating page to create a book or course.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_101")
    ```
    
1. Fill in a title and URL. Select "In your browser on Leanpub". We will change this to "Using Git and Github" shortly.

    ```{r, echo=FALSE, fig.alt='The title is Programming 101, the url is programming101. The In your browser on Leanpub box is selected.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_107")
    ```

1. Ensure you have selected the "FREE" plan.

    ```{r, echo=FALSE, fig.alt='The FREE checkout option has been selected.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_116")
    ```
    
1. Click "Sign up for the Free plan".

    ```{r, echo=FALSE, fig.alt='The FREE checkout option has been selected.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_116")
    ```
    
1. Once you have the course link, you should send this link to an editor of your organization. For example, you'd send https://leanpub.com/course_admin/leanpub/programming101.

