
Leanpub has both free and paid plans for authors. However to publish programmatically using a GitHub repository, you will need to be part of a paid plan or paid organizational plan.

1. Check your user menu. If you see an organization listed, you are probably set up correctly. 

    ```{r, echo=FALSE, fig.alt='The Fred Hutchinson Cancer Center is listed under the organization tab in the hamburger menu.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_7")
    ```
    
1. If you do not see an organization listed, you should contact your plan administrator and have them add you to the organizational account using directions below. Alternatively, you can use a personal paid account.
 
    ```{r, echo=FALSE, fig.alt='The Fred Hutchinson Cancer Center is not listed under the organization tab in the hamburger menu.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_15")
    ```

:::: {.notice}
- [Instructions for adding an Author](https://hutchdatascience.org/Using_Leanpub/add-organization-author.html)
- [Instructions for adding an Editor](https://hutchdatascience.org/Using_Leanpub/add-organization-editor.html)
::::
