
:::: {.warning}
_Before proceeding you should:_

1. Make sure that you have verified your email. Go to https://leanpub.com/author_dashboard/courses/unpublished and click the link to resend a verification email if you haven't yet verified your account.

    ```{r, echo=FALSE, fig.alt='If our email has not been verified, we get a landing page that requests we do this. There is a link to resend verification.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_89")
    ```
::::

1. Click on the hamburger menu, click on "Organization", and click the correct organization from the list. 

    ```{r, echo=FALSE, fig.alt='The organization tab is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_7")
    ```
    
1. Select the "Courses" tab and select "Create a new course".

    ```{r, echo=FALSE, fig.alt='The courses tab and create a new course button are highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_206")
    ```

1. On the new course page, make sure "write it yourself" is selected.

    ```{r, echo=FALSE, fig.alt='The write it yourself option is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_214")
    ```
    
1. Fill in a title and URL. Select "Using Git and Github".

    ```{r, echo=FALSE, fig.alt='The title is Programming 201, the url is programming201. The Using Git and GitHub writing mode box is selected.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b34b732d40_2_0")
    ```

1. Select "Add to plan".

    ```{r, echo=FALSE, fig.alt='The add to plan button at the bottom of the page is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b34b732d40_2_16")
    ```


