
:::: {.warning}
You must be editor to add another editor to an organization.
::::

Adding an editor to an organization makes it easy for them to add and update courses. Editors can always create a book or course in the organization, as well as invite authors to it.

1. Click on the hamburger menu, click on "Organization", and click the correct organization from the list. 

    ```{r, echo=FALSE, fig.alt='The organization tab is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_7")
    ```
    
1. Click on the "Editors" tab and select "Add an Editor".

    ```{r, echo=FALSE, fig.alt='The editors tab and add an editor button are highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_25")
    ```

1. Fill out the new editor's email and click "Invite Editor".

    ```{r, echo=FALSE, fig.alt='The username or email field is filled with collaborator at university.edu and the invite editor button is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_37")
    ```
    
:::: {.warning}
Invitations can only be sent to users who already have a Leanpub account.
::::

