
You will need to follow a few steps to get a certificate of completion in Leanpub.

:::: {.warning}
Before moving on you should:

1. Make sure that you have completed any quizzes for the course and are happy with your score.

1. Make sure that your name is filled out in your profile at https://leanpub.com/user_dashboard/settings. Otherwise, your certificate will be completed by "anonymous"!

    ```{r, echo=FALSE, fig.alt='The name "Fred Hutch" has been filled out on the user profile page.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_0")
    ```
::::

1. Go to your course homepage. You can find your course homepage by going to https://leanpub.com/user_dashboard/courses and clicking on the correct course.

1. Click on "Complete Course". You will be able to see your scores.
 
    ```{r, echo=FALSE, fig.alt='The Complete Course button on the course homepage is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1BQxrVYdKZTbpCaF-i_q9w7s9x034lEXpQZDU-Sl09cs/edit#slide=id.g162fb43cc93_0_28")
    ```
    
 1. Click on "Generate Certificate". Your certificate will be emailed to you!
 
    ```{r, echo=FALSE, fig.alt='The Generate Certificate button on the course summary page is highlighted.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1BQxrVYdKZTbpCaF-i_q9w7s9x034lEXpQZDU-Sl09cs/edit#slide=id.g162fb43cc93_0_32")
    ```
    
