Use the following steps to create a new Leanpub account.

1. Click on the hamburger menu on the top right and click the "Sign Up" button.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Click on the 'Sign up' button to start the account making process."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_1")
    ```

1. Fill out your name and email. Choose a username and password and click "Create Account".

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Click on the 'Sign up' button to start the account making process."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_1")
    ```

1. Confirm you are logged in. You should see your name above your email address.

    ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Click on the 'Sign up' button to start the account making process."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_18")
    ```

:::: {.warning}
It is very important that you fill in your real name, otherwise it won't appear on your completion certificate later!
::::
