
Leanpub has both free and paid plans for authors. However, you will need to be part of a paid plan or paid organizational plan. This will enable you to publish programmatically using a GitHub repository.

1. Check your user menu. If you see an organization listed, you are set up as an editor. 

    ```{r, echo=FALSE, fig.alt='The Fred Hutchinson Cancer Center is listed under the organization tab in the hamburger menu.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_7")
    ```
    
1. If you do not see an organization listed, and you believe you should be an editor, you should contact an editor or administrator from your organization and have them add you to the organizational account. If you believe you should be an author, you can also request this.
 
    ```{r, echo=FALSE, fig.alt='The Fred Hutchinson Cancer Center is not listed under the organization tab in the hamburger menu.', out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1b1ea0f5d51_0_15")
    ```

