
You can start a course on Leanpub and come back at any time. First, click on the course you want to take. Click "Add Course to Cart". You will need to do this even if you take the course for free.

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_40")
```

Click "Checkout with Free Purchase" if you are taking the course for free.

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_47")
```

Click "Complete Free Purchase".

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_54")
```

This takes you back to the home page, which can be a bit confusing!

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_61")
```

You can get back to the course by clicking the hamburger menu, selecting "Library", and "Courses". You can also go directly to https://leanpub.com/user_dashboard/courses.

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_68")
```

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_75")
```

Click on the course, and click "Go to course".

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_89")
```

Click "Start the Course".

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Leanpub home page."}
ottrpal::include_slide("https://docs.google.com/presentation/d/1nKVYtTsawTHSxMun69U3GO9xT_xSQsJjTEabEb1qAuU/edit#slide=id.g1a357f576b0_0_99")
```



